\section*{Press Coverage of Research}
\years{7. 2021}``December Issue Out Now!" \textit{Methods Blog}. (\textcolor{RoyalBlue}{\href{https://methodsblog.com/2021/12/02/december-issue-out-now-2/}{https://methodsblog.com/2021/12/02/december-issue-out-now-2/}}) by Stephenson, I. (2021, December 2).

\pubspace

\years{6. 2021}``Neil Garg, UCLA students, his daughters win Royal Society of Chemistry Horizon Prize" \textit{UCLA Newsroom}. (\textcolor{RoyalBlue}{\href{https://newsroom.ucla.edu/dept/faculty/neil-garg-ucla-students-his-daughters-win-royal-society-of-chemistry-horizon-prize}{https://newsroom.ucla.edu/dept/faculty/neil-garg-ucla-students-his-daughters-win-royal-society-of-chemistry-horizon-prize}}) by Wolpert, S. (2021, November 23).

\pubspace

\years{5. 2021}``Winner: 2021 Horizon Prize for Education" \textit{Royal Society of Chemistry News}. (\textcolor{RoyalBlue}{\href{https://www.rsc.org/prizes-funding/prizes/2021-winners/molecular-educators/}{https://www.rsc.org/prizes-funding/prizes/2021-winners/molecular-educators/}}) by Royal Society of Chemistry. (2021, November 23).

\pubspace

\years{4. 2021}``2021 Royal Society of Chemistry Horizon Prize for Education" \textit{UCLA Chemistry \& Biochemistry News}. (\textcolor{RoyalBlue}{\href{https://www.chemistry.ucla.edu/news/2021-royal-society-chemistry-horizon-prize-education}{https://www.chemistry.ucla.edu/news/2021-royal-society-chemistry-horizon-prize-education}}) by Jennings, P. (2021, November 23).

\pubspace

\years{3. 2021}``High-Stakes testing vs. anxiety and metacognition." \textit{Teacher Toolkit}. \\ (\textcolor{RoyalBlue}{\href{https://www.teachertoolkit.co.uk/2021/03/30/test-anxiety/}{https://www.teachertoolkit.co.uk/2021/03/30/test-anxiety/}}) by McGill, R. M. (2021, March 30).

\pubspace

\years{2. 2020}``Early Career Research Day winner improves neural network training for biological research." \textit{UCLA Institute for Digital Research \& Education}. (\textcolor{RoyalBlue}{\href{https://idre.ucla.edu/featured/early-career-research-day-winner-improves-neural-network-training-for-biological-research}{https://idre.ucla.edu/featured/early-career-research-day-winner-improves-neural-network-training-for-biological-research}}) by Ventura, K. (2020, July 1).

%\pubspace
\newpage

\years{1. 2018}``Student-developed tool brings 3D molecular models to smartphone screen." \textit{The Daily Bruin}. \\ (\textcolor{RoyalBlue}{\href{https://dailybruin.com/2018/07/30/student-developed-tool-brings-3d-molecular-models-to-smartphone-screen}{https://dailybruin.com/2018/07/30/student-developed-tool-brings-3d-molecular-models \\ -to-smartphone-screen}}) by Nakahara, E. (2018, July 30).