\section*{Conference Presentations and Talks}
\textit{*Presenting Author, **Supervised Undergraduate Student, \dag{} Equal Contribution}\\

\years{30. 2022}Kearley, J. R.*, Richmond, L. L., \textbf{Schwartz, S. T.}, \& Hargis, M. B. (2022, November). \textit{Take a load off: Examining partial and complete cognitive offloading of medication information.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 63rd Annual Meeting in Boston, MA, USA. November 19.

\pubspace

\years{29. 2022}\textbf{Schwartz, S. T.*}, Madore, K. P., \& Wagner, A. D. (2022, November). \textit{Readiness-to-remember: On the relationship between recognition memory, recollection precision, and moment-to-moment fluctuations in preparatory sustained attention.} \textbf{\underline{Poster}} presented at the 51st Annual Meeting of the Society for Neuroscience in San Diego, CA, USA. November 13.

\pubspace

\years{28. 2022}Bhardwaj, N.*\textsuperscript{,}**\textsuperscript{,}\dag, Tuli, A.**\textsuperscript{,}\dag, \textbf{Schwartz, S. T.}, Harrison, M. B., \& Wagner, A. D. (2022, November). \textit{Exploring the role of discrete vs. continuous perceptual context shifts during encoding on episodic memory.} \textbf{\underline{Poster}} presented at the Stanford University Symbolic Systems 2022 Summer Research Fair in Stanford, CA, USA. October 10.

\pubspace

\years{27. 2022}Tuli, A.*\textsuperscript{,}**\textsuperscript{,}\dag, Bhardwaj, N.**\textsuperscript{,}\dag, \textbf{Schwartz, S. T.}, Harrison, M. B., \& Wagner, A. D. (2022, August). \textit{Exploring the role of discrete vs. continuous perceptual context shifts during encoding on episodic memory.} \textbf{\underline{Poster}} presented at the Stanford University PsychSummer 2022 Poster Session in Stanford, CA, USA. August 18.

\pubspace

\years{26. 2022}Tran, T. T.*, Madore, K. P., Hsu, S. C., \textbf{Schwartz, S. T.}, \& Wagner, A. D. (2022, April). \textit{Lapses in attention predict memory variability in younger and older adults.} \textbf{\underline{Poster}} presented at the 29th Annual Meeting of the Cognitive Neuroscience Society in San Francisco, CA, USA. April 24.

\pubspace

\years{25. 2021}\textbf{Schwartz, S. T.*}, Siegel, A. L. M, \& Castel, A. D. (2021, November). \textit{Burgers over broccoli: Enhanced visuospatial memory for high-calorie foods.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 62nd Annual Meeting online. November 5.

\pubspace

\years{24. 2021}Perillo, M.*\textsuperscript{,}**\textsuperscript{,}\dag, \textbf{Schwartz, S. T. \dag}, \& Alfaro, M. E. (2021, May). \textit{Geographical relationships of coral reef fish color pattern geometry and speciation rates.} \textbf{\underline{Poster}} presented at the 24th Annual UCLA Biology Research Symposium in Los Angeles, CA, USA. May 26. \textbf{\textit{*Awarded 2nd Place for Best Poster*}}

\pubspace

\years{23. 2021}Brar, N. K.*\textsuperscript{,}**, \textbf{Schwartz, S. T.}, Silaj, K. M., \& Castel, A. D. (2021, May). \textit{A classroom study: Student attitudes and anxiety during a pandemic.} \textbf{\underline{Talk}} presented at the UCLA Undergraduate Research \& Creativity Showcase in Los Angeles, CA, USA. May 25.

\pubspace

\years{22. 2021}Brar, N. K.*\textsuperscript{,}**, \textbf{Schwartz, S. T.}, Silaj, K. M., \& Castel, A. D. (2021, May). \textit{A classroom study: Student attitudes and anxiety during a pandemic.} \textbf{\underline{Talk}} presented at the 30th Annual UCLA Psychology Undergraduate Research Conference in Los Angeles, CA, USA. May 14.

\pubspace

\years{21. 2021}\textbf{Schwartz, S. T.*} (2021, April). \textit{College students’ anxiety, preparedness, and perceptions of remote learning effectiveness during COVID-19: A classroom study.} \textbf{\underline{Talk}} presented at the National Center for the Integration of Research, Teaching and Learning Network Teaching-as-Research Conference. April 15.

\pubspace

\years{20. 2021}Karan, E. A.* \dag, \textbf{Schwartz, S. T. \dag}, Perillo, M.**, \& Alfaro, M. E. (2021, January). \textit{Evolutionary and functional consequences of sexually dimorphic color pattern diversity in Labrid fishes.} \textbf{\underline{Talk}} presented at the UCLA Department of Ecology \& Evolutionary Biology EcoEvoPub Seminar Series. January 14.

\pubspace

\years{19. 2021}\textbf{Schwartz, S. T.*}, Tsai, W. L. E., Karan, E. A., \& Alfaro, M. E. (2021, January). \textit{Charisma: An R tool to automatically determine discrete color classes for high-throughput color pattern analysis.} \textbf{\underline{Talk}} presented at the Society for Integrative and Comparative Biology (SICB) Virtual Annual Meeting. January 3.

\pubspace

\years{18. 2021}\textbf{Schwartz, S. T.*}, \& Alfaro, M. E., (2021, January). \textit{Sashimi: Automatic high-throughput pipeline for organismal image segmentation using deep learning.} \textbf{\underline{Poster}} presented at the Society for Integrative and Comparative Biology (SICB) Virtual Annual Meeting. January 3.

\pubspace

\years{17. 2021}Karan, E. A.* \dag, \textbf{Schwartz, S. T. \dag}, Perillo, M.**, \& Alfaro, M. E. (2021, January). \textit{It’s not just a phase: Evolutionary and functional consequences of sexually dimorphic color pattern diversity in Labrid fishes.} \textbf{\underline{Talk}} presented at the Society for Integrative and Comparative Biology (SICB) Virtual Annual Meeting. January 3.

\pubspace

\years{16. 2021}Weller, H. I.*, \textbf{Schwartz, S. T.}, Karan, E. A., \& Lord, N. P. (2021, January). \textit{Recolorize: a flexible R package for color classification.} \textbf{\underline{Talk}} presented at the Society for Integrative and Comparative Biology (SICB) Virtual Annual Meeting. January 3.

\pubspace

\years{15. 2020}\textbf{Schwartz, S. T.* \dag}, Silaj, K. M.* \dag, Brar, N. K.**, \& Castel, A. D. (2020, December). \textit{Anxiety, preparedness, and students’ perceptions of remote learning effectiveness during COVID-19.} \textbf{\underline{Talk}} presented at CogFog, Bjork Learning and Forgetting Lab. December 11.

\pubspace

\years{14. 2020}\textbf{Schwartz, S. T.* \dag}, Silaj, K. M.* \dag, Siegel, A. L. M., \& Castel, A. D. (2020, November). \textit{Examining the effects of test anxiety on metacognitive performance.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 61st Annual Meeting online. November 21. \textbf{\textit{*J. Frank Yates Student Conference Award recipient for supporting diversity \& inclusion in cognitive psychology*}}

\pubspace

\years{13. 2020}Siegel, A. L. M.* \dag, \textbf{Schwartz, S. T.* \dag}, \& Castel, A. D. (2020, November). \textit{Selective memory disrupted in intra-modal dual-task encoding conditions.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 61st Annual Meeting online. November 19.

\pubspace

\years{12. 2020}\textbf{Schwartz, S. T.* \dag}, Siegel, A. L. M.\dag, \& Castel, A. D. (2020, November). \textit{Selective memory disrupted in intra-modal dual-task encoding conditions.} \textbf{\underline{Talk}} presented live at the Virtual Bay Area Memory Meeting (BAMM!). November 12.

\pubspace

\years{11. 2020}Silaj, K. M.* \dag, \textbf{Schwartz, S. T.* \dag}, Siegel, A. L. M., \& Castel, A. D. (2020, September). \textit{Test anxiety and metacognitive performance in the classroom.} \textbf{\underline{Poster}} presented at the 2020 UC Psychology Teaching \& Learning Virtual Conference online. September 18.

\pubspace

\years{10. 2020}Siegel, A. L. M.*, \textbf{Schwartz, S. T.}, \& Castel, A. D. (2020, April). \textit{Age-related differences in local and global metacognitive accuracy in a visuospatial selectivity task.} \textbf{\underline{Poster}} accepted to be presented at the Cognitive Aging Conference in Atlanta, GA, USA. April 16. \textit{*Cancelled due to COVID-19*}

\pubspace

\years{9. 2019}\textbf{Schwartz, S. T.*}, \& Alfaro, M. E. (2019, November). \textit{High-throughput phenoscaping using deep learning for accurate automatic instance segmentation of fish images.} \textbf{\underline{Poster}} presented at the UCLA Institute for Digital Research \& Education Early Career Researcher Day in Los Angeles, CA, USA. November 20. \textbf{\textit{*Awarded 1 of 4 Best Poster Awards of 40 posters*}}

\pubspace

\years{8. 2019}Siegel, A. L. M.* \dag, \textbf{Schwartz, S. T.* \dag}, \& Castel, A. D. (2019, November). \textit{Memory and metamemory for the location of items: The effects of information importance and encoding difficulty.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 60th Annual Meeting in Montr\'eal, Quebec, Canada. November 16.

\pubspace

\years{7. 2019}Whatley, M. C.* \dag, \textbf{Schwartz, S. T.* \dag}, Block, J. B., Siegel, A. L. M., \& Castel, A. D. (2019, November). \textit{One bad apple: Visual memory and misinformation for the Apple logo.} \textbf{\underline{Poster}} presented at the Psychonomic Society's 60th Annual Meeting in Montr\'eal, Quebec, Canada. November 15.

\pubspace

\years{6. 2019}\textbf{Schwartz, S. T.*}, Karan, E. A., \& Alfaro, M. E. (2019, May). \textit{Using machine learning to quantify color pattern diversity in Butterflyfishes (Chaetodontidae).} \textbf{\underline{Poster}} presented at the 22nd Annual UCLA Biology Research Symposium in Los Angeles, CA, USA. May 22.

\pubspace

\years{5. 2019}\textbf{Schwartz, S. T.*}, Siegel, A. L. M., \& Castel, A. D. (2019, May). \textit{Risks and rewards: Memory for positive and negative item-location associations.} \textbf{\underline{Poster}} presented at the 22nd Annual UCLA Undergraduate Research Poster Day in Los Angeles, CA, USA. May 21. \textbf{\textit{*UCLA Dean's Research Prize Nominee*}}

\pubspace

\years{4. 2019}\textbf{Schwartz, S. T.*}, Siegel, A. L. M., \& Castel, A. D. (2019, May). \textit{Risks and rewards: Memory for positive and negative item-location associations.} \textbf{\underline{Poster}} presented at the 28th Annual UCLA Psychology Undergraduate Research Conference in Los Angeles, CA, USA. May 10.

\pubspace

\years{3. 2019}\textbf{Schwartz, S. T.*}, Siegel, A. L. M., \& Castel, A. D. (2019, May). \textit{Memory for positive and negative item-location associations.} \textbf{\underline{Poster}} presented at Whittier College's 17th Annual Psi Chi Psychology Undergraduate Research Conference in Whittier, CA, USA. May 4.

\pubspace

\years{2. 2019}Karan, E. A.* \dag, \& \textbf{Schwartz, S. T.* \dag} (2019, May). \textit{Quantitative approaches to studying color pattern evolution.} \textbf{\underline{Invited Guest Lecture}} given at Claremont McKenna College, W. M. Keck Science Center Department of Biology in Claremont, CA, USA. May 2.

\pubspace

\years{1. 2019}\textbf{Schwartz, S. T.*} (2019, May). \textit{Risks and rewards: Memory for positive and negative item-location associations.} \textbf{\underline{Talk}} for Highest Departmental Honors Thesis Seminar given at the UCLA Department of Psychology in Los Angeles, CA, USA. May 1.