\section*{Publications}
\subsection*{Peer-Reviewed Journal Articles}
\years{10. 2021}Richmond, L. L., Kearley, J., \textbf{Schwartz, S. T.}, \& Hargis, M. B. (Registered Reports In-Principle Acceptance). Take a load off: Examining partial and complete cognitive offloading of medication information. Stage 1 Registered Report In-Principle Acceptance. \textit{Cognitive Research: Principles and Implications}.

\pubspace

\years{9. 2021}Silaj, K. M., \textbf{Schwartz, S. T.}, Castel, A. D., \& McDonough, I. M. (in press). Is the future bright or bleak? Assessing past and future outlooks across the adult lifespan. \textit{Gerontology and Geriatric Medicine}.

\pubspace

\years{8. 2021}\textbf{Schwartz, S. T.}, \& Alfaro, M. E. (in press). \textit{Sashimi}: A toolkit for facilitating high-throughput organismal image segmentation using deep learning. \textit{Methods in Ecology and Evolution}.

\pubspace

\years{7. 2021}Snedden, C. E.*, Makanani, S. K.*, \textbf{Schwartz, S. T.}, Gamble, A., Blakey, R. V., Borremans, B., Helman, S. K., Espericueta, L., Valencia, A., Endo, A., Alfaro, M. E., \& Lloyd-Smith, J. O. (2021). SARS-CoV-2: Cross-scale insights from ecology and evolution. \textit{Trends in Microbiology, 29}(7), 593-605.\\
\textcolor{RoyalBlue}{\href{https://doi.org/10.1016/j.tim.2021.03.013}{doi.org/10.1016/j.tim.2021.03.013}}
\\ \textit{*Equal Contribution}

\newpage

\years{6. 2021}Siegel, A. L. M., \textbf{Schwartz, S. T.}, \& Castel, A. D. (2021). Selective memory disrupted in intra-modal dual-task encoding conditions. \textit{Memory \& Cognition}. \textcolor{RoyalBlue}{\href{https://doi.org/10.3758/s13421-021-01166-1}{doi.org/10.3758/s13421-021-01166-1}}

\pubspace

\years{5. 2021}Silaj, K. M., \textbf{Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2021). Test anxiety and metacognitive performance in the classroom. \textit{Educational Psychology Review}. \textcolor{RoyalBlue}{\href{https://doi.org/10.1007/s10648-021-09598-6}{doi.org/10.1007/s10648-021-09598-6}}

\pubspace

\years{4. 2020}Whatley, M. C., Siegel, A. L. M., \textbf{Schwartz, S. T.}, Silaj, K. M., \& Castel, A. D. (2020). Younger and older adults' mood and expectations regarding aging during COVID-19. \textit{Gerontology and Geriatric Medicine, 6}, 1-9. \textcolor{RoyalBlue}{\href{https://doi.org/10.1177/2333721420960259}{doi.org/10.1177/2333721420960259}}

\pubspace

\years{3. 2020}\textbf{Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2020). Strategic encoding and enhanced memory for positive value-location associations. \textit{Memory \& Cognition, 48}, 1015-1031. \\ \textcolor{RoyalBlue}{\href{https://doi.org/10.3758/s13421-020-01034-4}{doi.org/10.3758/s13421-020-01034-4}}

\pubspace

\years{2. 2019}Alfaro, M. E., Karan, E. A., \textbf{Schwartz, S. T.}, \& Shultz, A. J. (2019). The evolution of color pattern in butterflyfishes (Chaetodontidae). \textit{Integrative and Comparative Biology, 59}(3), 604-615.\\ \textcolor{RoyalBlue}{\href{https://doi.org/10.1093/icb/icz119}{doi.org/10.1093/icb/icz119}}

\pubspace

\years{1. 2018}Dang, J., Lin, B., Yuan, J., \textbf{Schwartz, S. T.}, Shah, R. M., \& Garg, N. K. (2018). Smart access to 3D structures. \textit{Nature Reviews Chemistry, 2}(7), 95-96. \textcolor{RoyalBlue}{\href{https://doi.org/10.1038/s41570-018-0021-y}{doi.org/10.1038/s41570-018-0021-y}}

\subsection*{Manuscripts Under Review}
\textbf{Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (under review). Burgers over broccoli: Prioritization of high-calorie food illustrations in human visuospatial memory. Manuscript under review.

\pubspace

Siegel, A. L. M.*, \textbf{Schwartz, S. T.*}, \& Castel, A. D. (under review). Metacognitive monitoring diminishes value selectivity in visuospatial memory. Manuscript under review.
\\ \textit{*Equal Contribution}

\pubspace

Murphy, D. H., Silaj, K. M., \textbf{Schwartz, S. T.}, Rhodes, M. G., \& Castel, A. D. (under review). An own-race bias in the recall of associative information. Manuscript under review.

\pubspace

Murphy, D. H., \textbf{Schwartz, S. T.}, \& Castel, A. D. (under review). Responsible retrieval: The dynamics of free recall when responsibly remembering. Manuscript under review.

\pubspace

Siegel, A. L. M., \textbf{Schwartz, S. T.}, Eich, T. S., \& Castel, A. D. (under review). The role of encoding and retrieval strategies on prioritization in memory in younger and older adults. Manuscript under review.

\subsection*{Manuscripts In Preparation}
\textbf{Schwartz, S. T.}, Tsai, W. L. E., Karan, E. A., \& Alfaro, M. E. (in prep). \textit{Charisma}: an R tool to automatically determine discrete color classes for high-throughput color pattern analysis. Manuscript in preparation.

\pubspace

\textbf{Schwartz, S. T.}, Silaj, K. M., Brar, N. K., \& Castel, A. D. (in prep). College students’ anxiety, preparedness, and perceptions of remote learning effectiveness during COVID-19: A classroom study. Manuscript in preparation.

\pubspace

Siegel, A. L. M., \textbf{Schwartz, S. T.}, \& Eich, T. S. (in prep). Knowledge of health-related information across the adult lifespan: Is error correction dependent on confidence? Manuscript in preparation.

\pubspace

Whatley, M. C., \textbf{Schwartz, S. T.}, Block, J. B., \& Castel, A. D. (in prep). One bad apple: Visual memory and misinformation for the Apple logo. Manuscript in preparation.